Instructions for developing new pages for the MarineOmics webpage

### 2023-01-17 submissions_instructions.Rmd
added section on in text citations, and some re-formatting. Also added code output to Sam's sections

```{r setup, echo = FALSE, message = FALSE}
library(knitr)
knitr::opts_chunk$set(cache = TRUE)
library(knitcitations)
library(kableExtra)
opts_chunk$set(fig.width = 10,
               fig.height = 5,
               cache = FALSE)
cite_options(citation_format = "pandoc", max.names = 3, style = "html", 
             hyperlink = "to.doc")
```

@@

## RMarkdown formatting basics
One of the strengths of .Rmd documents is their versatility. They can hold everything from code (not only in R but in other languages), formatted text, figure outputs, and more. Basically, code must be enclosed within 'code chunks' and anything outside of code chunks will be read as text, similar to a basic text file.

@@

\* Other options exist for code chunk output which can be explored online and in other .Rmd scripts in this repository.
<br>

@@

````
```{r setup} `r ''`
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, cache = TRUE) 
library(knitr)
library(knitcitations)
library(kableExtra)
knitr::opts_chunk$set(fig.width = 10, fig.height = 5) #setting the dimensions for figure outputs in a different line of code for cleanliness
cite_options(citation_format = "pandoc", max.names = 3, style = "html", 
             hyperlink = "to.doc") #setting format for in-text citations for the references section at the bottom of the page
```
````
\* Note the "cache = " option. When set to "true" R will cache all of the output created from knitting the RMarkdown document. This is especially useful for pages with heavy computation that take a long time to knit.
<br>

@@

- As with writing code, any text symbol that codes for something, such as a \# or a \* must be escaped with a backslash (\\) if you just want to use the symbol itself. <br>
- **\#**: *Outside of a code chunk*, pound signs dictate the size and organizational level of the text. A single \# will make large text and a main section in the navigation window. Two \#\# will make slightly smaller text and a sub-section in the navigation window. <br>
  + For example, the "RMarkdown formatting" text and category was created with "\# RMarkdown formatting" while the "code chunks" subcategory was created with "\#\# code chunks."<br>
- **\***: Asterisks are used to bold and italicize when surrounding texts. Use \*\***two asterisks to bold**\*\* and \**one asterisk*\* to italicize.<br>
- **\<br>**: adds a line break <br>
- **\<hr />**: adds a horizontal line across the page <br>

### **installing & loading packages**
If you will be using any R packages for your information page or tutorial, it's a good idea to highlight them toward the beginning of your page, including code for installing them. Here's an example from the RADseq tutorial:<br>
<br>
*If you would like to run the R code examples that are scattered throughout the guide (recommended but not required!), you will need to install some R packages. Only need to run this code once:*  
```{r, eval=F}
install.packages("tidyverse")
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
#the BiocManager package facilitates the installation of packages from the Bioconductor project
BiocManager::install("SeqArray")
BiocManager::install("SNPRelate")
```
### **caching**
If your page includes any code that takes a long time to run, please set "cache = TRUE" in the knitr::opts_chunk$set command in your global code chunk.

@@

### **insert a table**

@@

### **insert an image**

```{r, echo = FALSE, out.height = "40%", fig.align = "center", }

@@

For illustrative purposes, here is a simple and famous equation

$$
E = mc^2
$$

@@

As an example of a more complex equation, here is an equation for the t-statistic

$$
t = \frac{\overline{x_{1}}-\overline{x_{2}}}
{\sqrt{(s^2(
\frac{1}{n_{1}} + \frac{1}{n_{2}}
))}}
$$

### **in-text citations from your .bib**

RADseq can produce insightful analyses even in the absencee of data, if missing values are handled properly [@Tripp2017-cp].

@@

### **running code in another language such as bash - Katherine/Sam**

@@

## **References**

>>>>

```{r #setup, echo = FALSE, message = FALSE}
library(knitr)
knitr::opts_chunk$set(
	fig.height = 5,
	fig.width = 10,
	cache = FALSE
)
library(knitcitations)
library(kableExtra)
opts_chunk$set(fig.width = 10,
               fig.height = 5,
               cache = FALSE)
cite_options(citation_format = "pandoc", max.names = 3, style = "html", 
             hyperlink = "to.doc")
```

@@

## Formatting basics
One of the strengths of .Rmd documents is their versatility. They can hold everything from code (not only in R but in other languages), formatted text, figure outputs, and more. Basically, code must be enclosed within 'code chunks' and anything outside of code chunks will be read as text, similar to a basic text file.

@@

\* Other options exist for code chunk output which can be explored online and in other .Rmd scripts in this repository.

@@

<a id="cite_options"></a>
````
```{r setup} `r ''`
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, cache = TRUE) 
library(knitr)
library(knitcitations)
library(kableExtra)
knitr::opts_chunk$set(fig.width = 10, fig.height = 5) #setting the dimensions for figure outputs in a different line of code for cleanliness
cite_options(citation_format = "pandoc", max.names = 3, style = "html", 
             hyperlink = "to.doc") #setting format for in-text citations for the references section at the bottom of the page
```
````
\* Note the "cache = " option. When set to "true" R will cache all of the output created from knitting the RMarkdown document. This is especially useful for pages with heavy computation that take a long time to knit.

#### *including code from another language*
We can also run code such as bash in an R script by modifying the code chunk header as below: <br>

````
```{bash, eval = FALSE} `r ''`

```
````
<br>

@@

- As with writing code, any text symbol that codes for something, such as a \# or a \* must be escaped with a backslash (\\) if you just want to use the symbol itself. <br>
- **\#**: *Outside of a code chunk*, pound signs dictate the size and organizational level of the text. A single \# will make large text and a main section in the navigation window. Two \#\# will make slightly smaller text and a sub-section in the navigation window. <br>
  + For example, the "RMarkdown formatting" text and category was created with "\# RMarkdown formatting" while the "code chunks" subcategory was created with "\#\# code chunks."<br>
- **\***: Asterisks are used to bold and italicize when surrounding texts. Use \*\***two asterisks to bold**\*\* and \**one asterisk*\* to italicize.<br>
- **\<br>**: adds a line break <br>
- **\<hr />**: adds a horizontal line across the page

### **in-text citations from your .bib**
In-text citations can be made throughout the document that will automatically add a reference to your reference section via the following steps: <br>

- add your citations to the RCN_site-Nov05.bib document via your reference manager
- add the line 'bibliography: RCN_site-Nov05.bib' to your header at the top of the .Rmd document, which looks like this:
````
---
title: "Instructions for developing new pages for the MarineOmics webpage"
bibliography: RCN_site-Nov05.bib
---
````
- include the 'cite-options' chunk in your 'setup' code chunk. See the initial ['r setup' chunk](#cite_options) above for the syntax of the 'cite_options' command.

You can add Bibtex references to the file RCN_site-Nov05.bib, and then refer to them in your RMarkdown by adding bibliography: RCN_site-Nov05.bib to the header and citing them in the RMarkdown document. Check out existing pages for examples.

RADseq can produce insightful analyses even in the absence of data, if missing values are handled properly [@Tripp2017-cp].

### **installing & loading packages**
If you will be using any R packages for your information page or tutorial, it's a good idea to highlight them toward the beginning of your page, including code for installing them. Here's an example from the RADseq tutorial:<br>
<br>
*If you would like to run the R code examples that are scattered throughout the guide (recommended but not required!), you will need to install some R packages. Only need to run this code once:*  
```{r, eval=F}
install.packages("tidyverse")
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
#the BiocManager package facilitates the installation of packages from the Bioconductor project
BiocManager::install("SeqArray")
BiocManager::install("SNPRelate")
```

### **caching**
If your page includes any code that takes a long time to run, please set "cache = TRUE" in the knitr::opts_chunk$set command in your global code chunk.

@@

### **insert a table**
*text in .Rmd **(not in a code chunk)***:
````
| Term A | Term B | Term C | Term D | Term E | Term F | Term G |
| :--- | :--- | :--- | :--- | :--- | :--- | :--- |
| xxx | xxx | xxx | xxx | xxx | xxx | xxx |  
| yyy | yyy | yyy | yyy | yyy | yyy | yyy | 
| zzz | zzz | zzz | zzz | zzz | zzz | zzz | 
````

*knitted output*:

@@

### **insert an image**
*code chunk in .Rmd*:

````
```{r, echo = TRUE, include = TRUE, out.height = "40%", fig.align = "center"} `r ''`

```
````

*knitted output*:
```{r, echo = TRUE, include = TRUE, out.height = "40%", fig.align = "center", }

@@

For illustrative purposes, here is a simple and famous equation. <br>
*syntax in .Rmd*:
````
$$
E = mc^2
$$
````

@@

*knitted output*:
$$
E = mc^2
$$
<br>

As an example of a more complex equation, here is an equation for the t-statistic: <br>
*syntax in .Rmd*:
````
$$
t = \frac{\overline{x_{1}}-\overline{x_{2}}}
{\sqrt{(s^2(
\frac{1}{n_{1}} + \frac{1}{n_{2}}
))}}
$$ 
````

*knitted output*:
$$
t = \frac{\overline{x_{1}}-\overline{x_{2}}}
{\sqrt{(s^2(
\frac{1}{n_{1}} + \frac{1}{n_{2}}
))}}
$$

@@

@@

## References
